---
title: 'Activity 4: Visualize Graph Data'
author: "GT Account Name: abriel3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Inspect

Name of network dataset: bitcoin-otc   
Description: A network that stores the reputations of individuals who trade Bitcoin on the Bitcoin OTC platform.  
Link: http://snap.stanford.edu/data/soc-sign-bitcoinotc.html  
  

```{r results='hide', echo=FALSE, message=FALSE}
#install.packages("igraph")
library(igraph)
btc <- read.csv("soc-sign-bitcoinotc.csv", header=TRUE)
btc_g <- graph.data.frame(btc, directed=TRUE)
```
Tail of vertices:  
```{r echo=FALSE}
tail(V(btc_g))
```
Sample of 10 edges:  
```{r echo=FALSE}
E(btc_g)[sample(1:ecount(btc_g), 10)]
```  
Mean degree of nodes:  
```{r echo=FALSE}
mean(degree(btc_g, v = V(btc_g), mode = c("all"),
            loops = TRUE, normalized = FALSE))
```
Mean degree distribution:  
```{r echo=FALSE}
mean(degree_distribution(btc_g, cumulative = FALSE))
```  
  
##Visualization:  
The graph below shows a subset of 10 traders in the bitcoin-otc network, where arrows indicate direction of who rated who, and vertex size represents the betweenness centrality of each vertex.

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# X6 is SOURCE
# X2 is TARGET
# X4 is RATING
# X1289241911.72836 is TIMESTAMP

# Getting subset of 10 nodes
btc_g_sub <- subgraph(btc_g, c(1:10))
plot(btc_g_sub, vertex.size=betweenness(btc_g_sub))
```

##References:  

**Citation required for use of dataset,** S. Kumar, F. Spezzano, V.S. Subrahmanian, C. Faloutsos. Edge Weight Prediction in Weighted Signed Networks. IEEE International Conference on Data Mining (ICDM), 2016.
